Draft-assinment1

### 2017-02-19 Draft-xuezhou-sjb.Rmd
update

#5. Summary of variables<a id="variablesummary"></a>
##5.1 Individual variable summary

###5.1.1 School
####5.1.1.1. State
State variable has 59 levels, which include 55 states in the United States, as well as......... From the following frequncy table, we see that California has the most University-equivalent institutions across the nation, followed by Texas and Ner York. It has about 800 universities! A bar chart is plotted below to show the top states with the most universities. Then summary of frequency table also shows that the state having the least university only has one, and 50% of state has more than 132 universities in the state.
```{r, message=FALSE}

@@

####5.1.1.2. Predominant Degree
Then we analyze the type of degree universities mainly offer. There are four types of degree taken into accout: Certificate-degree, Associate's degree, Bachelor's degree, and Graduate Degree. About 5% of the population are classified in terms of the predomiant degree they offer.  43.2% offer Certificate degree as their predominant degree, 27.3% predominantly offer Bachelor degree and only 4.23% are classified as Graduate degree predominant.

@@

####5.1.1.3. Control of Institution
In addition to State and predominant degree, control of institution is another categorical variable in the dataset. The label of Control is to indicate whether or not a institution is institution is privately owned and whether or not it is a for-profit organization. There are three levels of this variable: Public, Private Nonprofit, and Private-profit. Public school is assumed to be non-profit so it was not further divided into two subgroups. Below we show the percentage summary of each category and a bar char is plotted to facilitate understanding. About 50% out of all institution are private for-profit university, which is the *most dominant type*. Public and Private Nonprofit are pretty tie in terms of number of observation in each category.

@@

###5.1.2 Student Body
####5.1.2.1 Percentage first-generation students<a id="5.1.2.1"></a>
This element identifies the share of federally aided students at the institution who report that they are first generaion on the FAFSA (Free Application for Federal Student Aid). First generation students are defined as sudents in which neither parents completed college.

@@

###5.1.4 Financial Aid 
####5.1.4.1 Percentage of undergraduates who receive a Pell Grant<a id="5.1.4.1"></a>

@@

###5.1.5 Earning
####5.1.5.1 Median family income in real 2015 dollars<a id="5.1.5.1"></a>
This elemnt is recording the median family income of students, one of the undergraduate student demographics for earnings cohorts.

@@

##6.8 cost and median debts with earning
Next, we analyze the relationship between the amount the debt and post-graduation earning. There are variable in the dataset to summarize the median amount for student body, one for students who already graduated and one for students who have not completed their study. We decide debts for students who have not completed to study in this problem, since it may can be used as a predictor in the future modeling. First, we use scatter plot to visualize the relationship between earning and the amount of debts, the plot clearly shows a positive relationship. Then we further calculate pearson correlation to confirm our hypothesis. The resulting coefficient 0.44 indicatesa moderate linear relationship between earning and debts.

@@

##6.9 default with earning

@@

##6.10 degree type vs. earning

@@

##6.11 predominant degree, control  and earning after 6 year of entry
The following plot shows two factor variables (predominant degree award variable and control variable) associated with one numeric variable (MD_EARN_WNE_P6: Median earnings of students working and not enrolled 6 years after entry. Our team uses the function geom_tile()[ggplot2 package] to visualize the correlation matrix.

@@

##6.12 predominant degree + control (count)
The following plot shows the relationship between two factor variables (predominant degree award variable and control variable). Our team uses the function geom_bar() to map the counting values to y, ctrF variable to x and the preF variable to the fill of the bar.

@@

 #6.11 control + earning
The following plot shows one factor variable (control variable) associated with one numeric variable (MD_EARN_WNE_P6: Median earnings of students working and not enrolled 6 years after entry). We use the 
geom_violin() using the default scale = ???area??? argument and geom_boxplot() function to explore the relationship. The plot superimposed with boxplots shows side-by-side violin plots of median earnings of students working and not enrolled 6 years after entry according to different college types.

@@

#7. Findings and Conclusion

>>>>

#5. Summary of variables<a id="5"></a>
##5.1 Individual variable summary<a id="5.1"></a>

###5.1.1 School<a id="5.1.1"></a> 
####5.1.1.1. State<a id="5.1.1.1"></a> 
State variable has 59 levels, which include 55 states in the United States, as well as......... From the following frequncy table, we see that California has the most University-equivalent institutions across the nation, followed by Texas and Ner York. It has about 800 universities! A bar chart is plotted below to show the top states with the most universities. Then summary of frequency table also shows that the state having the least university only has one, and 50% of state has more than 132 universities in the state.
```{r, message=FALSE}

@@

####5.1.1.2. Predominant Degree<a id="5.1.1.2"></a> 
Then we analyze the type of degree universities mainly offer. There are four types of degree taken into accout: Certificate-degree, Associate's degree, Bachelor's degree, and Graduate Degree. About 5% of the population are classified in terms of the predomiant degree they offer.  43.2% offer Certificate degree as their predominant degree, 27.3% predominantly offer Bachelor degree and only 4.23% are classified as Graduate degree predominant.

@@

####5.1.1.3. Control of Institution<a id="5.1.1.3"></a> 
In addition to State and predominant degree, control of institution is another categorical variable in the dataset. The label of Control is to indicate whether or not a institution is institution is privately owned and whether or not it is a for-profit organization. There are three levels of this variable: Public, Private Nonprofit, and Private-profit. Public school is assumed to be non-profit so it was not further divided into two subgroups. Below we show the percentage summary of each category and a bar char is plotted to facilitate understanding. About 50% out of all institution are private for-profit university, which is the *most dominant type*. Public and Private Nonprofit are pretty tie in terms of number of observation in each category.

@@

###5.1.2 Student Body<a id="5.1.2"></a> 
####5.1.2.1 Percentage first-generation students<a id="5.1.2.1"></a>
This element identifies the share of federally aided students at the institution who report that they are first generaion on the FAFSA (Free Application for Federal Student Aid). First generation students are defined as sudents in which neither parents completed college.

@@

###5.1.4 Financial Aid<a id="5.1.4"></a>  
####5.1.4.1 Percentage of undergraduates who receive a Pell Grant<a id="5.1.4.1"></a>

@@

###5.1.5 Earning<a id="5.1.5"></a> 
####5.1.5.1 Median family income in real 2015 dollars<a id="5.1.5.1"></a>
This elemnt is recording the median family income of students, one of the undergraduate student demographics for earnings cohorts.

@@

##6.8 cost and median debts with earning<a id="6.8"></a> 
Next, we analyze the relationship between the amount the debt and post-graduation earning. There are variable in the dataset to summarize the median amount for student body, one for students who already graduated and one for students who have not completed their study. We decide debts for students who have not completed to study in this problem, since it may can be used as a predictor in the future modeling. First, we use scatter plot to visualize the relationship between earning and the amount of debts, the plot clearly shows a positive relationship. Then we further calculate pearson correlation to confirm our hypothesis. The resulting coefficient 0.44 indicatesa moderate linear relationship between earning and debts.

@@

##6.9 default with earning<a id="6.9"></a>

@@

##6.10 degree type vs. earning<a id="6.10"></a>

@@

##6.11 predominant degree, control  and earning after 6 year of entry<a id="6.11"></a> 
The following plot shows two factor variables (predominant degree award variable and control variable) associated with one numeric variable (MD_EARN_WNE_P6: Median earnings of students working and not enrolled 6 years after entry. Our team uses the function geom_tile()[ggplot2 package] to visualize the correlation matrix.

@@

##6.12 predominant degree + control (count)<a id="6.12"></a> 
The following plot shows the relationship between two factor variables (predominant degree award variable and control variable). Our team uses the function geom_bar() to map the counting values to y, ctrF variable to x and the preF variable to the fill of the bar.

@@

 #6.13 control + earning<a id="6.13"></a> 
The following plot shows one factor variable (control variable) associated with one numeric variable (MD_EARN_WNE_P6: Median earnings of students working and not enrolled 6 years after entry). We use the 
geom_violin() using the default scale = ???area??? argument and geom_boxplot() function to explore the relationship. The plot superimposed with boxplots shows side-by-side violin plots of median earnings of students working and not enrolled 6 years after entry according to different college types.

@@

#7. Findings and Conclusion<a id="7"></a>
